---
title             : "Our APA document for Lab 8"
shorttitle        : "Lab 8 APA document"

author: 
  - name          : "Cameron S. Kay"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1451 Onyx Street, Eugene, OR 97403"
    email         : "ckay@uoregon.edu"
  - name          : "Stefania Ashby"
    affiliation   : "1"
  - name          : "Ashley L. Miller"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"

abstract: |
  Here is an abstract. It is abstract but also specific. 
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "apa, papaja, science"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 6.5,
                      fig.height = 8.0)

library(papaja)
library(tidyverse)
library(ggplot2)
library(here)
library(rio)
library(janitor)

```

```{r load data}

star_data <- import(here("data", "star.csv"), 
                    setclass = "tbl_df")

star_data <- janitor::clean_names(star_data)

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

I am writing an introduction. @caprara2006teachers found some stuff. But other people have found other stuff [@zimmerman1990self].

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

Consistent with prior work

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
