---
title             : "Our APA document for Lab 8"
shorttitle        : "Lab 8 APA document"

author: 
  - name          : "Cameron S. Kay"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1451 Onyx Street, Eugene, OR 97403"
    email         : "ckay@uoregon.edu"
  - name          : "Stefania Ashby"
    affiliation   : "1"
  - name          : "Ashley L. Miller"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"

abstract: |
  Here is an abstract. It is abstract but also specific. 
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "apa, papaja, science"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 6.5,
                      fig.height = 8.0)

library(papaja)
library(tidyverse)
library(ggplot2)
library(here)
library(rio)
library(janitor)
library(knitr)

```

```{r load_data}

star_data <- import(here("data", "star.csv"), 
                    setclass = "tbl_df") %>%
              janitor::clean_names()

```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

I am writing an introduction. @caprara2006teachers found some stuff. But other people have found other stuff [@zimmerman1990self].

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis

# Results

Table 1. 

*Descriptive statistics for math and reading, grouped by sex and frl.* 
```{r create_table, results='asis'}
star_data %>%
  group_by(sex, frl) %>%
  summarize(math_mean = round(mean(tmathss), 2),
            math_sd = round(sd(tmathss), 2),
            rdg_mean = round(mean(treadss), 2),
            rdg_sd = round(sd(treadss),2)) %>%
  apa_table()
```

As shown in Table 1, the mean math and reading scores for boys with "yes" for
frl was lower than the mean math and reading scores for boys with "no" for frl.
In contrast, the mean math and reading scores for girls with "yes" for frl was
higher than the mean math and reading scores for girls with "no" for frl. For
both levels of frl, the mean math and reading scores were higher for girls than
boys. 

# Discussion

\newpage

# References
```{r create_r-references}
r_refs(file = "references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
