---
title             : "Our APA document for Lab 8"
shorttitle        : "Lab 8 APA document"

author: 
  - name          : "Cameron S. Kay"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1451 Onyx Street, Eugene, OR 97403"
    email         : "ckay@uoregon.edu"
  - name          : "Stefania R. Ashby"
    affiliation   : "1"
  - name          : "Ashley L. Miller"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"

abstract: |
  Here is an abstract. It is abstract but also specific. 
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "apa, papaja, science"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
figsintext        : yes

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 6.5,
                      fig.height = 8.0)

library(papaja)
library(tidyverse)
library(ggplot2)
library(here)
library(rio)
library(janitor)
library(knitr)

```

```{r load_data}

star_data <- import(here("data", "star.csv"), 
                    setclass = "tbl_df") %>%
              janitor::clean_names()

```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

I am writing an introduction. @caprara2006teachers found some stuff. But other people have found other stuff [@zimmerman1990self].

\newpage

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis

\newpage

# Results

As shown in Table 1, the mean math and reading scores for boys with "yes" for
frl was lower than the mean math and reading scores for boys with "no" for frl.
In contrast, the mean math and reading scores for girls with "yes" for frl was
higher than the mean math and reading scores for girls with "no" for frl. For
both levels of frl, the mean math and reading scores were higher for girls than
boys. 


```{r create_table, results='asis'}
star_data %>%
  group_by(sex, frl) %>%
  summarize(math_mean = round(mean(tmathss), 2),
            math_sd = round(sd(tmathss), 2),
            rdg_mean = round(mean(treadss), 2),
            rdg_sd = round(sd(treadss),2)) %>%
  apa_table(caption = "Descriptive statistics for math and reading, grouped by sex and frl.",
            placement = 'h') # placement 'h' puts the table exactly where it is in your layout.

```

As shown in Figure 1, there is a similar relationship between teacher experience and student performance on math for both groups of students. With more years of teaching experience, students do better on their math scores. However students who receive free/reduced priced meals (implying lower socioeconomic status) have an overall deficit compared to students with higher socioeconomic status, demonstrating that they are at a disadvantage from the beginning. 

```{r create plot, }
library(cowplot)
library(wesanderson)
pal <- wes_palette("Darjeeling1")

plot_data <- star_data %>% 
  mutate(frl = factor(frl, 
                          levels = c("yes",
                                     "no"))) %>% 
  group_by(frl)
 
ggplot(plot_data, aes(x = totexp, y = tmathss, color = frl)) +
  theme_apa(box = TRUE) + 
  geom_point(color = "grey70") +
  geom_smooth(method = 'lm') +
  scale_color_manual(name = "Lunch status",
                     values = pal[4:5],
                     breaks = c("yes", "no"),
                     labels = c("Free/Reduced Price Meals", "Paid Meals")) +
  labs(title = "Relation between teacher experience and math scores",
       subtitle = "Separate regression lines displayed by free/reduced price lunch status",
       x = "Teacher Experience (years)",
       y = "Total Math Scale Score") +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        title = element_text(size = 12),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10)) 

# Can't seem to get the figure on the page that I want it on in the text. 

```


\newpage

# Discussion

\newpage

# References
```{r create_r-references}
r_refs(file = "references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
